Project 1_Course5
=======================

Loading the data set And Calculating Number of steps for each day

```{r,echo=TRUE}
df<-read.csv("D:/All_coding_Activities/activity.csv")
df[is.na(df)]=0
tsteps<-tapply(df$steps,df$date,sum,na.rm=TRUE)
tsteps


```
Calculating Number of steps
```{r,echo=TRUE}
library(ggplot2)

dft<-data.frame(date=names(tsteps),steps=tsteps)
ggplot(dft,aes(date,steps))+geom_col()
```
Mean And Median of Total Number of steps Per Day
```{r,echo=TRUE}
tmean<-tapply(df$steps,df$date,mean,na.rm=TRUE)
tmedian<-tapply(df$steps,df$date,median,na.rm=TRUE)
print(data.frame(date=names(tmean),mean_steps=tmean))
print(data.frame(date=names(tmedian),median_steps=tmedian))


```
Printing the average steps per every 5 minute interval
```{r,echo=TRUE}
tavint<-tapply(df$steps,df$interval,mean)
print(tavint)
```
Plotting Timeseries for average across five minute breaks
```{r,echo=TRUE}
dftavint<-data.frame(date=names(tavint),avg_steps=tavint)
ggplot(dftavint,aes(date,avg_steps,group=1))+geom_line()
```
creating new variable in the dataframe weekdays
```{r,echo=TRUE}

df["weekday"]=weekdays(as.Date(df$date))
 for (i in 1:17568)
 {
   if(df[i,"weekday"]=="Monday"||df[i,"weekday"]=="Tuesday"||df[i,"weekday"]=="Wednesday"||
      df[i,"weekday"]=="Thursday"||df[i,"weekday"]=="Friday")
   {
     df[i,"weekdays"]="weekday"
   }
   else
   {
     df[i,"weekdays"]="weekend"
   }
 }
head(df)
```
Plotting the timeseries for average steps on weekdays and weekends
```{r,echo=TRUE}
dfsp<-split(df,df$weekdays)
wd<-dfsp$weekday
 we<-dfsp$weekend
 wda<-tapply(wd$steps,wd$interval,mean)
 wea<-tapply(we$steps,we$interval,mean)
 dfwd<-data.frame(date=names(wda),avg_steps=wda)
 dfwe<-data.frame(date=names(wea),avg_steps=wea)
 ggplot()+geom_line(dfwd,mapping=aes(date,avg_steps,group=1,color="red"))+geom_line(dfwe,mapping=aes(date,avg_steps,group=1,color="blue"))+scale_color_manual(labels = c("weekends", "weekdays"), values = c("blue", "red"))
```

